%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Javier Parada} & Email : jparada@worldbank.org\\
  https://www.paradajavier.com/ & Mobile : +1-240-302-3872 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Davis}{Davis, CA}
      {PhD in Agricultural and Resource Economics}{2011 -- 2018}
    \resumeSubheading
      {Centro de Investigaci\'on y Docencia Econ\'omicas}{Mexico City, Mexico}
      {MS in Economics}{2008 -- 2010}
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {The World Bank Development Data Group (DECDG)}{Washington, DC}
      {Junior Data Scientist}{May 2021 -- Present}
      \resumeItemListStart
        \resumeItem{World Development Indicators (WDI)}
          {Manage the curation, maintenance, update, and documentation of World Bank’s Environmental portfolio in the WDI, which includes:
           
          - Food, agriculture, fish production, land cover, and deforestation indicators by country, with updates automated as new data becomes available using FAO's FAOSTAT API.  

          - Greenhouse gas emissions by country, gas, and sector, updated each year from the Climate Watch's historical emissions database. 
          
          - Energy and electricity production and consumption indicators by country, per capita, and by fuel source. 
         
          - Biodiversity protection indicators related to the establishment of land and marine protected areas, updated each year in synchrony with the World Database on Protected Areas (WDPA). 
          
          - Calculation of global, national, and sub-national sea-level rise vulnerability indicators including percentage of land and population within 5 meters above sea level using digital elevation models. 
                              
          -  Other indicators that monitor progress towards the Sustainable Development Goals (SDG 6 on water, SDG 7 on energy, SDG 13 on climate change, SDG 14 on oceans, and SDG 15 on life on forests).
          
          -  For all of these, communicate indicator’s current methodology and changes in a shared repository, especially concerning handling of missing data and outliers, and the creation of aggregates and other derived indicators.}

        \resumeItem{Atlas of Sustainable Development Goals 2023}
          {Develop interactive website that inspires to discover and visualize progress towards achieving the SDGs (forthcoming). 
          
          - Develop storylines and visuals as co-author for the stories related to SDG 7 and SDG 14.}
      
        \resumeItem{Cross-support activities}
          {Maps, charts, and other dashboards for several teams, including requests for Country Climate and Development Reports (CCDRs). }
      \resumeItemListEnd

    \resumeSubheading
      {The World Bank}{Washington, DC}
      {Postdoctoral researcher}{July 2020 -- April 2021}
      \resumeItemListStart
        \resumeItem{Fellowship Program in Forced Displacement}{Sponsored by the DFID-UNHCR-World Bank program ``Building the Evidence on Forced Displacement: A Multi-Stakeholder Partnership".
        
        - Use of detailed georeferenced panel data to study land cover dynamics into and out of cropland in the Middle East as a result of conflict.}
        %\resumeItem{Deliver two co-authored World Bank Policy Research Working Papers to be submitted to peer reviewed academic journals following publication in the World Bank series}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Other recent projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Sovereign ESG Data Portal}
      {Cross-support on data management tasks for https://esgdata.worldbank.org/.}
    \resumeSubItem{Land Matters: Can Better Governance and Management of Scarcity Prevent a Looming Crisis in the Middle East and North Africa?}
      {Contributed land use change analysis and maps to flagship report (see http://hdl.handle.net/10986/38384).}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Stata, R, Tableau, Git, Matlab, R Shiny} \\
     \textbf{Libraries}{: pandas, geopandas, scikit-learn, numpy, matplotlib, pyplot, seaborn, leaflet, geemap} \\
     \textbf{GIS Tools}{: QGIS, Google Earth Engine} \\
    }}
 \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{:  Full Professional} \\
     \textbf{Spanish}{:  Native} \\
     \textbf{French}{:  Limited Working} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
